---
title: "tidytuesday_ceo_departures"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

library(tidytuesdayR)
library(tidyverse)



```

```{r}
tt <- tidytuesdayR::tt_load('2021-04-27')


departures <- tt$departures

departures %>% 
  mutate(departure_code_type = case_when(
    departure_code == 1 ~ "Involuntary - CEO death",
    departure_code == 2 ~ "Involuntary - CEO illness",
    departure_code == 3 ~ "Involuntary – CEO dismissed for job performance",
    departure_code == 4 ~ "Involuntary - CEO dismissed for legal violations or concerns",
    departure_code == 5 ~ "Voluntary - CEO retired",
    departure_code == 6 ~ "Voluntary - new opportunity (new career driven succession)",
    departure_code == 7 ~ "Other",
    departure_code == 8 ~ "Missing",
    departure_code == 9 ~ "Execucomp error",
  ))%>%
  count(departure_code,departure_code_type,fyear,sort=TRUE)%>%
  mutate(departure_code_type = fct_reorder(as.factor(departure_code_type),n),
         fyear = fct_reorder(as.factor(fyear),n))%>%
  ggplot(aes(departure_code_type,n,fill = fyear))+geom_col()+coord_flip()+
  labs(title = "Top reasons for CEO departures over the years",
       x = "Departure reason",
       y = "Count")




  ```
```


```{r}


departures %>%
  filter(departure_code >0)%>%
  mutate(departure_code_type = case_when(
    departure_code == 1 ~ "Involuntary - CEO death",
    departure_code == 2 ~ "Involuntary - CEO illness",
    departure_code == 3 ~ "Involuntary – CEO dismissed for job performance",
    departure_code == 4 ~ "Involuntary - CEO dismissed for legal violations or concerns",
    departure_code == 5 ~ "Voluntary - CEO retired",
    departure_code == 6 ~ "Voluntary - new opportunity (new career driven succession)",
    departure_code == 7 ~ "Other",
    departure_code == 8 ~ "Missing",
    departure_code == 9 ~ "Execucomp error",
  ))%>%
  group_by(departure_code,departure_code_type,fyear)%>%
  summarise(n = n())%>%
  group_by(fyear)%>%
  mutate(pct = n/sum(n))%>%
  ggplot(aes(fyear,pct,fill=departure_code_type))+geom_area()+
  labs(title = "Top reasons for CEO departures over the years",
       x = "% contribution of reason")





