---
title: "tidymodels_song_popularity"
output: html_document
date: "2023-11-20"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(tidymodels)
library(janitor)
library(GGally)
song_train <- read.csv('C:/Users/delhivery/Documents/R-projects/song_popularity/train.csv')%>%
  clean_names()

song_test <- read.csv('C:/Users/delhivery/Documents/R-projects/song_popularity/test.csv')%>%
  clean_names()


```

### EDA on the data 
1. No missing values 
2. 6 types of Genres 
3. Popularity does not vary much as per genre, we can probably drop this feature 
4. Popularity does not vary much as per year, we can probably drop this feature 
5. Other features seem to have strong corelation with popularity, lets try simple lin reg

```{r}
song_train %>% 
  glimpse()

song_train %>% 
  skimr::skim()


song_train %>% 
  ggplot(aes(popularity))+geom_histogram()+facet_wrap(~genre)+
  labs(title = 'Song popularity distribution by genre',
       subtitle = " Good old normal distribution")

song_train %>%
  group_by(genre)%>%
  summarise(avg_pop= mean(popularity))%>%
  mutate(genre = fct_reorder(genre, avg_pop))%>%
  ggplot(aes(avg_pop,genre))+geom_col()+
  labs(title = "Avg popularity by genre",
       subtitle = 'Doesnt vary much')


song_train %>% 
  group_by(released_year)%>%
  summarise(avg_pop= mean(popularity))%>%
  ggplot(aes(released_year,avg_pop))+geom_col()+
  labs(title = "Avg popularity by released_year",
       subtitle = 'slight decline in rating across years')
  
ggpairs(song_train %>% select(song_length,num_instruments,tempo,lyrical_content,popularity))



```

### Build model
1. Cross fold validation

```{r}
song_folds <- vfold_cv(song_train)
song_folds

```

2. Define recipe and model 

```{r}
song_rec <- recipe(popularity ~ song_length + num_instruments + tempo + 
                     lyrical_content + popularity , data = song_train)

song_spec <- 
  linear_reg()%>%
  set_engine('lm')

song_wf <- workflow()%>%
  add_recipe(song_rec)%>%
  add_model(song_spec)

```

3. Fit model and validate across folds
- Model seems to be robust 

```{r}
control_preds <- control_resamples(save_pred = TRUE)

song_results <- fit_resamples(song_wf,
                              resamples = song_folds,
                              control = control_preds)

song_results %>% 
  collect_metrics()

song_results %>%
  select(id,.predictions)%>%
  unnest()%>%
  ggplot(aes(.pred,popularity,color = id))+geom_point()+
  labs(title = 'Pred vs actual for all folds')


song_results %>% 
  select(id,.metrics)%>%
  unnest(cols = c(.metrics))%>%
  ggplot(aes(.estimate,id))+geom_col()+
  facet_wrap(~.metric)+
  labs(title = 'Metrics for individual resamples')

```


4. Final fit and prediction on test 

```{r}
song_final_fit <- fit(song_wf,data = song_train)

song_final_fit %>% 
  augment(song_test)


```


