---
title: "tidymodels_usa_housing"
output: html_document
date: "2023-11-16"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidymodels)
library(tidyverse)
library(janitor)
library(GGally)


usa_housing <- read_csv("c:/Users/delhivery/Documents/R-projects/USA_Housing.csv")%>%
  clean_names()


usa_housing %>%
  glimpse()


usa_housing %>% 
  skimr::skim()

```

### lets do some EDA first 
1. Price seems to be normally distributed 
2. all numerical variables seem to be highly correlated with price, we can try a linear regression model in this case 

```{r}

usa_housing %>% 
  ggplot(aes(price))+geom_histogram()


usa_housing %>% 
  select(- address)%>%
  ggpairs()



```

### Build model

1. Create splits and folds for validation 

```{r}
set.seed(1234)

usa_split <- initial_split(usa_housing,strata = price)
usa_training <- training(usa_split)
usa_testing <- testing(usa_split)


usa_folds <- vfold_cv(usa_training)
usa_folds

```

2. Create recipe and model 

```{r}
usa_rec <- recipe(price ~ avg_area_income + avg_area_house_age + avg_area_number_of_rooms +
                    avg_area_number_of_bedrooms +area_population, data = usa_training )

usa_spec <- linear_reg()%>%
  set_engine("lm")

usa_wf <- workflow()%>% 
  add_recipe(usa_rec)%>% 
  add_model(usa_spec)

```


3. Fit the model across folds and validate 


```{r}

control_preds <- control_resamples(save_pred = TRUE)

usa_fit <- fit_resamples(usa_wf,
                         resamples = usa_folds,
                         control = control_preds)


usa_fit %>% 
  collect_metrics()

usa_fit %>% 
  select(id,.predictions)%>% 
  unnest()%>% 
  ggplot(aes(.pred,price,color = id))+geom_point()+
  labs(title = 'Pred vs observed value for all folds - suggests that model is robust')

```


4. Final fit and prediction on testing set
- Final workflow model suggests that income, number of rooms & bedrooms has high impact on price

```{r}

usa_final_fit <- last_fit(usa_wf, usa_split)

usa_wf_final <- extract_workflow(usa_final_fit)

usa_testing %>% 
  select(price)%>% 
  cbind(predict(usa_wf_final,usa_testing,interval = 'confidence'))%>% 
  ggplot(aes(.pred,price))+geom_point()+
  labs(title = 'Pred vs observed value for final test set')


usa_testing %>% 
  select(price)%>% 
  cbind(predict(usa_wf_final,usa_testing,interval = 'confidence'))%>% 
  mutate(sq_errors = (.pred - price))%>%
  ggplot(aes(sq_errors))+geom_histogram()+
  labs(title = " Residual errors are normally distributed")

```



