---
title: "tidytuesday_summermovies"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

Exploring "Summer movies" data set from this weeks (2024-07-30) TidyTuesday datas et. 
The data this week comes from the Internet Movie Database.

Lets load the necessary packages, and download the data set.

```{r}

library(tidytuesdayR)
library(tidyverse)
library(janitor)

tidytues <- tidytuesdayR::tt_load('2024-07-30')

summer_movie_genres <- tidytues$summer_movie_genres
summer_movies <- tidytues$summer_movies

```

Lets explore the data 
1. Summer moview genres 
  - 2 columns, 1585 rows. 
  - 905 unique identifier of movies and 25 gneres of movies (some NAs exist). Many to many relationship
  - 1 movie can have multiple genres, at max 3
  - Drama, Comedy and Romance are the top 3 Genres 
  - And they are most commonly together as well 

```{r}
summer_movie_genres %>% 
  glimpse()

summer_movie_genres%>%
  count(tconst,genres,sort = TRUE)

summer_movie_genres%>%
  group_by(tconst)%>%
  summarise(n = n_distinct(genres))%>%
  arrange(-n)

summer_movie_genres %>% 
  filter(!is.na(genres))%>%
  group_by(genres)%>%
  summarise(n = n_distinct(tconst))%>%
  arrange(-n)%>%
  mutate(genres = fct_reorder(genres,n))%>%
  ggplot(aes(n,genres))+geom_col()+
  labs(title = "Count of moview Genre wise",
       y = "Genres",
       x = NULL)+
  theme_minimal()


summer_movie_genres %>% 
  group_by(tconst)%>%
  mutate(row = row_number(), n =n())%>%
  ungroup()%>%
  filter(n>2)%>%
  pivot_wider(names_from = row,values_from = genres)%>%
  unite("genre_combined",3:5,remove = FALSE)%>%
  group_by(genre_combined)%>%
  summarise(n_tconst = n_distinct(tconst))%>%
  ungroup()%>%
  arrange(desc(n_tconst))%>%
  mutate(genre_combined = fct_reorder(genre_combined,n_tconst))%>%
  slice_head(n=15)%>%
  ggplot(aes(n_tconst,genre_combined))+geom_col()+
  labs(title = "Combination of Genres appearing the most",
       y = "Genres",
       x = "Number of movies")+
  theme_minimal()


```

2. Summer movies
- More and more tiltes are released every year 
- Movie run-times are going down
- Variation in ratings have increased over the decades, probably because of number of ratings, can look into that data 
- Ratings and runtime dont show any relation though 
- Maximum movies belong to Drama / Romance / comedy genre, but Talk-Show,Documentary and Music have higher average ratings 

```{r}
summer_movies%>%
  glimpse()

summer_movies %>% 
  group_by(year)%>%
  summarise(title_count = n_distinct(tconst))%>%
  ggplot(aes(year,title_count))+geom_point()+
  geom_smooth()+
  labs(title = "Number of titles released every year since 1925",
       subtitle = "Clearly trending up",
       x = NULL, 
       y = NULL) +
  theme_minimal()


summer_movies %>% 
  group_by(year)%>%
  summarise(avg_runtime = mean(runtime_minutes))%>% 
  ggplot(aes(year,avg_runtime))+geom_point()+
  geom_smooth()+
  labs(title = "Average runtime in min per year",
       subtitle = "Clearly trending down",
       x = NULL, 
       y = NULL) +
  theme_minimal()


summer_movies %>% 
  group_by(year)%>%
  summarise(avg_rating = mean(average_rating))%>% 
  ggplot(aes(year,avg_rating))+geom_point()+
  geom_smooth()+
  labs(title = "Average ratings on IMDB have been flat",
       y = "Average IMDB rating", 
       x = NULL) +
  theme_minimal()

summer_movies %>% 
  filter(!is.na(year))%>%
  mutate(decade = year - year %% 10)%>%
  mutate(decade = as.factor(decade))%>%
  ggplot(aes(decade,average_rating,fill=decade))+geom_boxplot()+
  labs(title = "Variation in the ratings have gone up",
       y = "Average IMDB rating", 
       x = NULL, fill = NULL) +
  theme_minimal()+
  theme(legend.position = "None")


summer_movies %>% 
  filter(!is.na(year))%>%
  mutate(decade = year - year %% 10)%>%
  mutate(decade = as.factor(decade))%>%
  ggplot(aes(runtime_minutes,average_rating,color = decade))+geom_point()+
  facet_wrap(~decade)+
  geom_smooth()+
  labs(title = "Ratings vs Runtime min by decade",
       x = "Runtime in Min",
       y = "Average ratings")+
  theme_minimal()+
  theme(legend.position = "None")


summer_movie_genres %>%
  filter(!is.na(genres))%>%
  left_join(.,summer_movies %>% 
              select(tconst,average_rating),
            by = c('tconst'))%>%
  group_by(genres)%>%
  summarise (avg_rating = mean(average_rating))%>%
  mutate(genres = fct_reorder(genres,avg_rating))%>%
  ggplot(aes(avg_rating,genres))+geom_col()+
  labs(title = "Average ratings by genres",
       x = NULL, y = NULL)+
  theme_minimal()
  

```



