---
title: "tidytuesday_diwali_sales"
output: html_document
date: "2023-11-16"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
library(tidytuesdayR)
library(janitor)


tuesdata <- tidytuesdayR::tt_load('2023-11-14')
tuesdata

diwali_sales <- tuesdata$diwali_sales_data%>% clean_names()


diwali_sales %>% 
  glimpse()




```

### Lets explore the data first !
- Amount for 12 of the observations are missing out of 11251, we can ignore these rows 
- Data gives User - Product ID wise spend , 1250 users bought 2350 products 
- Central zone has highest number of orders and value as well 
- UP , MH, Karnataka , Delhi, MP - top 5 states 
- Food, Apparel, electronics, footware  - top 5 categories 
- Avg order value is similar across states, but varies greatly with product category 
- Female spend is higher 
- Age groups between 18 to 45, spending the maximum online 


```{r}


diwali_sales %>% 
  skimr::skim()

diwali_sales <- 
  diwali_sales %>% 
  filter(!is.na(amount))

diwali_sales%>% 
  ggplot(aes(amount))+geom_histogram()+
  labs(title = "Histogram of the amount spent")

diwali_sales%>% 
  group_by(zone)%>% 
  summarise(total_spend = sum(amount ))%>% 
  mutate(zone = fct_reorder(zone,total_spend))%>% 
  ggplot(aes(total_spend,zone, fill = zone))+geom_col()+
  labs ( title = 'Amount spent zone wise')


diwali_sales%>% 
  group_by(zone)%>% 
  summarise(total_orders = sum(orders ))%>% 
  mutate(zone = fct_reorder(zone,total_orders))%>% 
  ggplot(aes(total_orders,zone, fill = zone))+geom_col()+
  labs ( title = 'Number of orders zone wise')


diwali_sales%>% 
  group_by(zone,state)%>% 
  summarise(total_spend = sum(amount ))%>% 
  mutate(state = fct_reorder(state,total_spend))%>% 
  mutate(zone = fct_reorder(zone,total_spend))%>% 
  ggplot(aes(total_spend,state, fill = zone))+geom_col()+facet_wrap(~zone,scale = 'free_y')+
  scale_x_continuous(labels = scales :: comma)+
  labs ( title = 'Amount spent zone - state wise')


diwali_sales%>% 
  group_by(product_category)%>% 
  summarise(total_spend = sum(amount ))%>% 
  mutate(product_category = fct_reorder(product_category,total_spend))%>% 
  ggplot(aes(total_spend,product_category))+geom_col()+
  scale_x_continuous(labels = scales :: comma)+
  labs ( title = 'Amount spent product category wise')

diwali_sales %>% 
  group_by(gender)%>% 
  summarise(total_spend = sum(amount ))%>% 
  mutate(gender = fct_reorder(gender,total_spend))%>% 
  ggplot(aes(total_spend,gender))+geom_col()+
  scale_x_continuous(labels = scales :: comma)+
  labs ( title = 'Amount spent gender wise')

diwali_sales %>% 
  group_by(age_group)%>% 
  summarise(total_spend = sum(amount ))%>% 
  mutate(age_group = fct_reorder(age_group,total_spend))%>% 
  ggplot(aes(total_spend,age_group))+geom_col()+
  scale_x_continuous(labels = scales :: comma)+
  labs ( title = 'Amount spent age_group wise')

diwali_sales %>% 
  mutate(marital_status = as.factor(marital_status))%>%
  group_by(marital_status)%>% 
  summarise(total_spend = sum(amount ))%>% 
  ggplot(aes(total_spend,marital_status))+geom_col()+
  scale_x_continuous(labels = scales :: comma)+
  labs ( title = 'Amount spent marital_status wise')



## whats the ticket size 
diwali_sales %>% 
  mutate(amout_per_order = amount / orders )%>% 
  ggplot(aes(amout_per_order))+geom_boxplot()+facet_wrap(~zone)

diwali_sales %>% 
  mutate(amout_per_order = amount / orders )%>% 
  ggplot(aes(amout_per_order))+geom_boxplot()+facet_wrap(~product_category)




```

