---
title: "tidymodels_CDCdata"
output: html_document
date: "2023-11-27"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}

library(tidymodels)
library(tidyverse)
library(janitor)
library(GGally)

# read the data 

cdc_data <- read_csv("C:/Users/delhivery/Documents/R-projects/Nutrition__Physical_Activity__and_Obesity_-_Behavioral_Risk_Factor_Surveillance_System.csv")%>%
  clean_names()

cdc_data %>% 
  glimpse()


```


### Explore data 
1. data_value is seems to vary as per question and class / topic , about 5046 values are missing 
2. data is already stratified based on age, education, income, race etc. can use this column 



```{r}

cdc_data %>% 
  skimr::skim()


cdc_data %>% 
  ggplot(aes(data_value,education))+geom_boxplot()


cdc_data %>% 
  count(stratification_category1,stratification1)%>%
  view()
```

### clean the data 

```{r}

cdc_cleaned <-  cdc_data %>%
    filter(stratification1 != 'Total')%>%
    select(question_id,class_id,location_abbr,stratification_id1,data_value)%>%
    drop_na()

```


### Build a model 

1. Create data splits

```{r}

cdc_split <- initial_split(cdc_cleaned)

cdc_train <- training(cdc_split)
cdc_test <- testing (cdc_split)

cdc_folds <- vfold_cv(cdc_train)

```

2. Create recipe and model specs

```{r}

cdc_rec <- recipe( data_value ~ .,data = cdc_train)%>%
  step_dummy(all_nominal_predictors())

cdc_spec <- linear_reg()%>%
  set_engine('lm')

cdc_wf <- workflow()%>%
  add_recipe(cdc_rec)%>%
  add_model(cdc_spec)



```


3. Fit resamples 
- Model fits nicely 
- Class and Question have highest impact on the output variables, Location_ID does not matter much. This is interesting as it shows that output is not related to certain geographies 

```{r}

control_preds <- control_resamples(save_pred = TRUE)

cdc_results <- fit_resamples(cdc_wf,
                             resamples = cdc_folds,
                             control = control_preds)

cdc_results %>% collect_metrics()

cdc_results%>%
  select(id,.predictions)%>%
  unnest(.predictions)%>%
  ggplot(aes(.pred,data_value,color = id))+geom_point()


cdc_final_fitted <- last_fit(cdc_wf,cdc_split)

cdc_final_wf<- extract_workflow(cdc_final_fitted)


cdc_final_wf %>% 
  augment(cdc_test)%>%
  mutate(residuals = .pred - data_value)%>%
  ggplot(aes(residuals))+geom_histogram()
  

cdc_final_wf %>% 
  tidy()%>%
  mutate(term = fct_reorder(term,estimate))%>%
  ggplot(aes(estimate,term,fill = estimate<0))+geom_col()+
  theme(legend.position = "none")+
  labs(title = "Featuer importance")

```







