---
title: "tidymodels_lin-reg_1"
output: html_document
date: "2023-11-14"
editor_options: 
  chunk_output_type: console
---


```{r}
library(tidyverse)
library(janitor)
library(tidymodels)
library(GGally)

# Read the data 

ecom_customers <- read_csv("c:/Users/delhivery/Documents/R-projects/Ecommerce Customers.csv")%>%
  clean_names()



ecom_customers%>%
  glimpse()


```


## Lets explore the data first 
- all numerical variables seem to be normally distributed 
- lenght of membership seems to be highly correlated with yearly amount spent. Seems obvious as loyal customers would tend to send more 
- Apart from this, time spent on app & avg session lenght also has a higher correlation with amount spent as compared to time spent on website 
- yearly_amount_spent across different avatars seems have no predictive power 
- we can use all numerical predictors to build our model 




```{r}

ecom_customers %>% 
  skimr::skim()

ggpairs(ecom_customers %>% select(avg_session_length,time_on_app,time_on_website,length_of_membership,yearly_amount_spent))


ecom_customers %>% 
  group_by(avatar)%>%
  summarise(total_spend = sum(yearly_amount_spent))%>%
  arrange(-total_spend)%>%
  ggplot(aes(total_spend))+geom_histogram()



```


## Building the model 

1. Create splits, we will also build a cross fold validation 

```{r}
set.seed(1234)

ecom_split <- initial_split(ecom_customers,strata = yearly_amount_spent)
ecom_train <- training(ecom_split)
ecom_test <- testing(ecom_split)

ecom_folds <- vfold_cv(ecom_train)
ecom_folds



```


2. Build model specification and workflow 
- lets build a simple linear regression model workflow 

```{r}

# create recipe 

ecom_rec <- 
  recipe(yearly_amount_spent ~ avg_session_length + time_on_app + time_on_website + length_of_membership , data = ecom_train)

ecom_spec <- 
  linear_reg()%>%
  set_engine("lm")


ecom_wf <- 
  workflow()%>%
  add_recipe(ecom_rec)%>%
  add_model(ecom_spec)

```


3. Fit the model 

```{r}

control_preds <- control_resamples(save_pred = TRUE)

ecom_results <- 
  fit_resamples(ecom_wf,
                resamples = ecom_folds,
                control = control_preds)





```

4. Collect and analyze metrics 
- Model seems robust across all cross folds

```{r}

ecom_results%>%
  select(.predictions,id)%>%
  unnest()%>%
  ggplot(aes(.pred,yearly_amount_spent,color = id))+geom_line()+
  labs(title= "Predicted value vs observed value for all cross folds on training set",
       subtitle = " model results seem robust")


collect_metrics(ecom_results)


```

5. Final prediction
- final workflow shows time_on_app has a far greater influence on the amount spent. Tech teams should focus on building app features more than web features and customers should be redirected to app than website


```{r}

final_fitted <- last_fit(ecom_wf,ecom_split)

collect_metrics(final_fitted)

final_wf <- extract_workflow(final_fitted)

ecom_test %>%
  select(yearly_amount_spent)%>%
  cbind(predict(final_wf, ecom_test, interval = 'confidence'))%>%
  ggplot(aes(yearly_amount_spent,.pred))+geom_point()+
  labs(title= ' Final predicted vs observed on test set')



```

